### 2011-05-11 trunk/htdocs/user.tex
docs: added comments on wall lubrication
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1362 40876441-3496-0410-a613-a2fca35b2ae2

This sets the minimum cell list width. The cell list has a number
of purposes: it is used to compute colloid-colloid interactions
at $O(N)$, but it is also used in the message passing episodes
for the colloids. This key must be set and there must be at least
two cells per processor domain.

@@

These values set the $x-$component of the wall velocity at
$z = z_{min}$ and $z = z_{max}$, respectively. Like all
velocities, these values must respect the low Mach number
constraint $u_x < c_s$.

@@

Note that if something more complicated is required, for example,
an equilibration at zero shear followed by a run with shear, one
needs to be careful how this is arranged. The code works out the
current displacement of the planes by computing $U_{LE} t$, where
$t$ is the current time step. A shear run should then start from
$t = 0$, otherwise an offset is required. At the moment this cannot
be done via the input.

>>>>

This sets the minimum cell list width. This key must be set and there
must be at least two cells per processor domain. If the minimum does
not capture the specified interactions, a fatal error will result.
For spherical particles, the minimum width will typically be
$2a_h + h_c$ where $h_c$ is an interaction cut-off distance.

In the case where very large particles are required, it can be useful
to switch of the cell list. This is done via

\inputkey{colloid\_cell\_list\_interactions no}

The constraint in this case is that $2a_h + h_c < L_{local}$, ie.,
there is effectively one cell in each local domain. (In practice,
the constraint is slightly tighter than this if larger halo regions
are in effect.) This option
should not be required in normal circumstances.

@@

These values set the $x-$component of the wall velocity at
$z = z_{\min}$ and $z = z_{\max}$, respectively. Like all
velocities, these values must respect the low Mach number
constraint $u_x < c_s$.

There is a further option for use with the special case in which
top and bottom walls in the $z-direction$ are used to drive a shear
flow (typically with the top speed positive and the bottom speed
negative). The key

\inputkey{boundary\_shear\_init}

may be switched on (set to 1) to provide initialisation of the
LB distributions appropriate for the specified shear rate based
on a linear velocity profile in the $z-$direction. The default
is to initialise the fluid at rest.

\subsubsection{Flat wall lubrication correction}

It is possible to prevent colloids colliding with the flat boundary walls
by adding the correction to the normal component of the lubrication
force. The general form of this correction is
\begin{equation}
\mathbf{F}_{\mathrm{lub}} = -6\pi \eta a_h^2
%({\textstyle \frac{1}{h} - \frac{1}{h_c}})
(1/h - 1/h_c)
\mathbf{u} . \mathbf{r}.
\end{equation}
Here, $h$ is the surface to surface separation, and $h_c$ is the cutoff
distance beyond which the correction is not applied. The relative
velocity (assuming the wall is not moving) and normal separation are
$\mathbf{u}$ and $\mathbf{r}$ respectively.

The cutoff distance can be set from the input via

\inputkey{boundary\_lubrication\_rcnormal 0.1}

where the value is (strictly) set via calibration, cf. the hydrodynamic
radius. In general, the cutoff is between zero and 0.5 lattice spacing,
and can be smaller for larger particles. Because the wall velocity is
fixed, this force correction should cause no stability issues in the
colloid velocity update (provided a colloid's initial position is not
very close to the wall). By default the cutoff $h_c = 0$.

@@

The code works out the
current displacement of the planes by computing $U_{LE} t$, where
$t$ is the current time step. A shear run should then start from
$t = 0$, otherwise an offset is required.

\inputkey{LE\_time\_offset}

It is often convenient to run an equilibration with no shear, and
then to start an experiment after some number of steps. This
key allows you to offset the start of the Lees-Edwards motion.
It should then take the value of the start time (in time steps)
corresponding to the restart at the end of the equilibration
period. You also need to take this value into account when unrolling
the output.
